Progress Report

### 2023-09-21 Docs/ProgressReport.Rmd
try to calculate subject-wise AUC
GLMMadaptive results

```{r, fig.height=3, fig.width=9}
df %>% filter(id %in% skip_id) %>% 
  ggplot()+
  geom_point(aes(x=sind, y=Y), size = 0.2)+
  facet_wrap(~id)+
  geom_vline(xintercept = c(540))
```

@@

- when fitting model with **random intercept + slope** on the same full training set (even after scaling covariates): Error: vector memory exhausted (limit reached?). 
- when fitting model with **only random intercept** on the same full training set: Error regarding a large coefficient value. One fix is to re-scale covariates. So I re-scaled minute index by dividing them by J, so the range is within (0, 1], and tried again. This fitting procedure took 20.72 minutes to finish
- Out-of-sample prediction took 12.18 minutes. About 0.007 minute per subject.
- I'd also exclude the subjects with failed Laplace approximation here. 
- Should I calculate AUC subject-wise?

@@

@@

- What would be the reference method to compare our performance to? Original GLMMadaptvie perhaps is feasible on teh entire dataset. But what should we use if we wanna do sub-sample comparison? Should we even do that for this data application (or simulation alone)? 
- There are still three folks with numeric problem! Shall we extend the observation track even more? I suspect that may cause still the same issue just on different subjects. 
- Is interplation really necessary? It does not improve performance very much but consumes time. Also, should I try more sophisticated methods for grid extension?

>>>>

```{r, fig.height=6, fig.width=9}
df %>% filter(id %in% skip_id) %>% 
  ggplot()+
  geom_point(aes(x=sind, y=Y), size = 0.2)+
  facet_wrap(~id)+
  geom_vline(xintercept = c(540))
```

@@

- when fitting model with **random intercept + slope** on the same full training set (even after scaling covariates): Error: vector memory exhausted (limit reached?). 
- when fitting model with **only random intercept** on the same full training set: Error regarding a large coefficient value. One fix is to re-scale covariates. So I re-scaled minute index by dividing them by J, so the range is within (0, 1], and tried again. This fitting procedure took 20.72 minutes to finish
- Out-of-sample prediction took 12.18 minutes. About 0.007 minute per subject.
- I'd also exclude the subjects with failed Laplace approximation here.

@@

```{r}
df_test_full2 <- df_test_full %>%
  filter(id %in% rand_id2)%>%
  select(id, sind, Y)

df_test_full2$pred_t540 <- df_test_full2$pred_t780 <- df_test_full2$pred_t1020 <- NA 
for(i in rand_id2){
  df_test_full2[df_test_full2$id==i & df_test_full2$sind>540, "pred_t540"]<- adglmm_pred_t540$newdata2 %>% filter(id ==i) %>% select(pred)

  df_test_full2[df_test_full2$id==i & df_test_full2$sind>780, "pred_t780"]<- adglmm_pred_t780$newdata2 %>% filter(id ==i) %>% select(pred)

  df_test_full2[df_test_full2$id==i & df_test_full2$sind>1020, "pred_t1020"]<- adglmm_pred_t1020$newdata2 %>% filter(id ==i) %>% select(pred)
}

# colSums(is.na(df_test_full2))
```

```{r, warning=FALSE}
df_test_full2 %>% 
  mutate_at(vars(pred_t540, pred_t780, pred_t1020), 
            function(x)exp(x)/(1+exp(x))) %>%
  ggplot()+
    geom_line(aes(x=sind, y = pred_t540, col = "9am"))+
    geom_line(aes(x=sind, y = pred_t780, col = "1pm"))+
    geom_line(aes(x=sind, y = pred_t1020, col = "5pm"))+
    geom_point(aes(x=sind, y = Y, col = "Outcome"), size = 0.2)+
    facet_wrap(~id)+
    labs(x = "Time", y = "Estimated latent function (probablity scale)")
```

@@

- What would be the reference method to compare our performance to? Original GLMMadaptvie perhaps is feasible on teh entire dataset. But what should we use if we wanna do sub-sample comparison? Should we even do that for this data application (or simulation alone)? 
- There are still three folks with numeric problem! Shall we extend the observation track even more? I suspect that may cause still the same issue just on different subjects. 
- Is interplation really necessary? It does not improve performance very much but consumes time. Also, should I try more sophisticated methods for grid extension? 
- Should I calculate subject-wise AUC and average them? But some subjects are all zero within the predictio window, making AUC for this single subjects impossible to calculate...
